---
title: "Discussion2_Pandya.R"
author: "Harsh Pandya"
date: "1/24/2022"
output: html_document
---

```{r}
#Libraries Used for the same
library(tidyverse)
library(dplyr)
library(readr)
library(RColorBrewer)
library(readxl)

#DataSet
library(readxl)
Discussion2_Sales <- read_excel("/Users/HARSH/Documents/R Proj ALY6000/DataSets/Discussion2_Sales.xlsx")
View(Discussion2_Sales)

```
#Basic Descriptive Statistics for Price 
```{r}


#Average Value or Mean
Mean_Price=mean(Discussion2_Sales$Price,na.rm=TRUE) #For Null values
print(paste("The Mean of Price is","$",round(Mean_Price,2)))

```
```{r}

#Standard Deviation
SD_Price=sd(Discussion2_Sales$Price,na.rm=TRUE) #For Null values
print(paste("The SD is","$",round(SD_Price,2)))


```

```{r}
#Median 
Median_Price=median(Discussion2_Sales$Price,na.rm=TRUE) #For Null values
print(paste("The Median is","$",round(Median_Price,2)))

```

```{r}

#Minimum Value
MinValue_Price=min(Discussion2_Sales$Price,na.rm=TRUE) #For Null values
print(paste("The Min Value of Price is","$",round(MinValue_Price,2)))

```
```{r}

#Maximum Value
MaxValue_Price=mean(Discussion2_Sales$Price,na.rm=TRUE) #For Null values
print(paste("The Max Value of Price is","$",round(MaxValue_Price,2)))

```
```{r}

#Range
Range_Price=(MaxValue_Price-MinValue_Price)
print(paste("The Range of Price is","$",round(Range_Price,2)))

```

```{r}

#25th Quantile
First_Quantile=quantile((Discussion2_Sales$Price),0.25)
print(paste("The 25th Quantile is","$",round(First_Quantile,2)))


```
```{r}

#Matrix

Summary_Statistics=c(round(Mean_Price, 2),round(SD_Price, 2),round(Median_Price, 2),round(MinValue_Price, 2),round(MaxValue_Price,2),round(Range_Price,2),round(First_Quantile,2))

#Table Creation

Summary_Matrix=matrix(Summary_Statistics, nrow = 7, byrow = TRUE)

Statistics=c("Mean","Standard Deviation","Median","Minimum Value","Maximum Value","Range","25th Quantile")

colnames(Summary_Matrix)= "Price"
rownames(Summary_Matrix)= Statistics

knitr::kable(Summary_Matrix,caption = "TABLE (HARSH PANDYA)")
```
```{r}

#Histogram for Price

hist(Discussion2_Sales$Price,breaks = 15,
     main ="HISTOGRAM (Harsh Pandya)",
     ylab = "Distribution",
     xlab = "Price",
     col = terrain.colors(12),
     las=1,xaxp=c(0,5000,20))
```

```{r}

#Box Plot for Price 

boxplot(Discussion2_Sales$Price~Discussion2_Sales$Product_Category,
        range = 4,col = brewer.pal(7,"Set1"),
        main="BOX PLOT (Harsh Pandya)",
        ylab= "PRODUCT CATEGORY",
        xlab= "($)PRICE",
        horizontal = TRUE,xaxp=c(0,5000,20),ylim=c(0,4000),cex.axis="0.75")

```

Price is the numerical value chosen by me.
As can be observed from the above distributions, there is a huge difference observed between the Maximum Value and Minimum Value of prices. The gap herein represent a varied range. For the same reason we can observe a positive standard deviation
The Histogram represents that the maximum chunk of data prices are observed between the range of $0 to $2000, and a very few of them rise above $3000.
The Bar Plot highlights the price with respect to the defined Product Categories, representing that the office supplies consist of the higher end prices.